Visualising metagenome differences

### 2023-11-20 analysis/metagenome.Rmd
workflowr::wflow_publish(files = c("analysis/index.Rmd", "analysis/metagenome.Rmd"))

There we go :) Which MAGs are those?
```{r}
amph_pos_tax_cat |> filter(str_detect(Species, 'Acidihalobacter'))
```

@@

```{r}
count_diffs |> filter(`Posidonia australis` <100)
```

@@

```{r}
genessplit |> filter(gene == 'acdS') |> left_join(amph_pos_tax, by=c('sample', 'MAG'), multiple = 'any')
```
Lots of unknown taxonomies :(

>>>>

There we go :) Which MAGs are those?
```{r}
amph_pos_tax_cat |> filter(str_detect(Species, 'Acidihalobacter')) |> knitr::kable()

@@

```{r}
count_diffs |> filter(`Posidonia australis` <100) |> head() |> knitr::kable()
```

@@

```{r}
genessplit |> filter(gene == 'acdS') |> left_join(amph_pos_tax, by=c('sample', 'MAG'), multiple = 'any') |> knitr::kable()
```
Lots of unknown taxonomies :(
